---
title: "Figure S5"
author: "Lieke Vlaar"
date: "05/10/2021"
output: html_document
---
Initiate the necessary libraries:

```{r, message = FALSE, warning = FALSE}
library(ggpmisc)
library(extrafont)
library(ggplot2)
library(tidyverse)
library(dplyr)
library(plotrix)
```

Load the necessary functions:

```{r, message = FALSE, warning = FALSE}
source("scripts/hatch_calc.R")
source("scripts/hatch_summ.R")
```

## Atropine

All other, supplementary, plots, showing what was tried

atropine, first get overview of everything sorted by date:

```{r atrop1, fig.width = 10, fig.height = 7, message = FALSE, warning = FALSE}
atrop_c <- hatch_calc(input = "input/combined_per_treatment_atropine.csv")
atrop_s <- hatch_summ1(input = "input/combined_per_treatment_atropine.csv")

source("scripts/overviewplot.R")

p_atrop <- overview(atrop_c, atrop_s)

p_atrop

#make overview separately for solA, TRDh, TRDl

atrop_c_solA <- atrop_c[grep("TRD|PRE|8c|PRD|8b", atrop_c$treatment, ignore.case = T, invert = T),]
atrop_s_solA <- atrop_s[grep("TRD|PRE|8c|PRD|8b", atrop_s$treatment, ignore.case = T, invert = T),]

p_atrop2 <- overview(atrop_c_solA, atrop_s_solA)
p_atrop2

atrop_c_TRDl <- atrop_c[grep("TRD_l", atrop_c$treatment, ignore.case = T),]
atrop_s_TRDl <- atrop_s[grep("TRD_l", atrop_s$treatment, ignore.case = T),]

p_atrop3 <- overview(atrop_c_TRDl, atrop_s_TRDl)
p_atrop3

atrop_c_TRDh <- atrop_c[grep("TRD_h", atrop_c$treatment, ignore.case = T),]
atrop_s_TRDh <- atrop_s[grep("TRD_h", atrop_s$treatment, ignore.case = T),]

p_atrop3 <- overview(atrop_c_TRDh, atrop_s_TRDh)
p_atrop3
```

Then filter on what to show (manually by making a new .csv file) and make supplemental figure plot:

```{r atrop2, fig.width = (5/12*11), fig.height = 3.5, message = FALSE, warning = FALSE}
atropc4 <- hatch_calc(input = "input/atropine_figs4.csv")
atrops4 <- hatch_summ3(input = "input/atropine_figs4.csv")

source("scripts/plot_grid_s4.R")

S4B <- plotgrid(c = atropc4, s = atrops4)
S4B + theme(axis.title.x = element_text(size = 10)) + xlab("atropine conc (mM)")
```

## 8Br-cGMP

```{r 8br, fig.width = (5/12*4), fig.height = 3.5, message = FALSE, warning = FALSE}
br8_c <- hatch_calc(input = "input/combined_per_treatment_8bcGMP.csv")
br8_s <- hatch_summ1(input = "input/combined_per_treatment_8bcGMP.csv")
p_br8 <- overview(br8_c, br8_s, xf = 50)
p_br8

#make final figure
bcg_c <- hatch_calc(input = "input/8bg.csv")
bcg_s <- hatch_summ4(input = "input/8bg.csv")
S4A <- plotgrid(bcg_c, bcg_s) + scale_x_discrete(labels = c("8Br-cGMP 0.2 mM",
                                                           "8Br-cGMP 1.0 mM",
                                                           "8Br-cGMP 2.5 mM",
                                                           "8Br-cGMP 5.0 mM"))
S4A
```




## Akt inhibitor IV

```{r akt1, fig.width = 10, fig.height = 7, message = FALSE, warning = FALSE}
akt_c <- hatch_calc(input = "input/combined_per_treatment_AktinhibitorIV.csv")
akt_s <- hatch_summ1(input = "input/combined_per_treatment_AktinhibitorIV.csv")
p_akt <- overview(akt_c, akt_s, xf = 1)
p_akt

#make separate overviews for solA, TRD_l and TRD_h

akt_c_solA <- akt_c[grep("TRD|PRE|8c|PRD|8b", akt_c$treatment, ignore.case = T, invert = T),]
akt_s_solA <- akt_s[grep("TRD|PRE|8c|PRD|8b", akt_s$treatment, ignore.case = T, invert = T),]

p_akt2 <- overview(akt_c_solA, akt_s_solA, xf = 1)
p_akt2

akt_c_TRDl <- akt_c[grep("TRD_l", akt_c$treatment, ignore.case = T),]
akt_s_TRDl <- akt_s[grep("TRD_l", akt_s$treatment, ignore.case = T),]

p_akt3 <- overview(akt_c_TRDl, akt_s_TRDl, xf = 1)
p_akt3

akt_c_TRDh <- akt_c[grep("TRD_h", akt_c$treatment, ignore.case = T),]
akt_s_TRDh <- akt_s[grep("TRD_h", akt_s$treatment, ignore.case = T),]

p_akt4 <- overview(akt_c_TRDh, akt_s_TRDh, xf = 1)
p_akt4

```

```{r akt2, fig.width = (5/12*13), fig.height = 3.5, message = FALSE, warning = FALSE}
aktiivc4 <- hatch_calc(input = "input/aktinhiv_figs4.csv")
aktiivs4 <- hatch_summ3(input = "input/aktinhiv_figs4.csv")

aktiivc4$conc_inh <- factor(aktiivc4$conc_inh, levels = c("0uM","10uM","25uM","50uM","100uM"), ordered = TRUE)
aktiivc4 <- aktiivc4[order(aktiivc4$conc_inh),]
aktiivs4$conc_inh <- factor(aktiivs4$conc_inh, 
                            levels = c("0uM","10uM","25uM","50uM","100uM"), 
                            ordered = TRUE)
aktiivs4 <- aktiivs4[order(aktiivs4$conc_inh),]

S4C <- plotgrid(c = aktiivc4, s = aktiivs4)
S4C + theme(axis.title.x = element_text(size = 10)) + xlab("Akt inh IV conc (uM)")
```

## LY294002

```{r ly1, fig.width = 10, fig.height = 7, message = FALSE, warning = FALSE}
ly_c <- hatch_calc(input = "input/combined_per_treatment_LY294002.csv")
ly_s <- hatch_summ1(input = "input/combined_per_treatment_LY294002.csv")
p_ly <- overview(ly_c, ly_s, xf = 1)
p_ly

#make separate overviews for solA, TRD_l and TRD_h

ly_c_solA <- ly_c[grep("TRD|PRE|8c|PRD|8b", ly_c$treatment, ignore.case = T, invert = T),]
ly_s_solA <- ly_s[grep("TRD|PRE|8c|PRD|8b", ly_s$treatment, ignore.case = T, invert = T),]

p_ly2 <- overview(ly_c_solA, ly_s_solA, xf = 1)
p_ly2

ly_c_TRDl <- ly_c[grep("TRD_l", ly_c$treatment, ignore.case = T),]
ly_s_TRDl <- ly_s[grep("TRD_l", ly_s$treatment, ignore.case = T),]

p_ly3 <- overview(ly_c_TRDl, ly_s_TRDl, xf = 1)
p_ly3

ly_c_TRDh <- ly_c[grep("TRD_h", ly_c$treatment, ignore.case = T),]
ly_s_TRDh <- ly_s[grep("TRD_h", ly_s$treatment, ignore.case = T),]

p_ly4 <- overview(ly_c_TRDh, ly_s_TRDh, xf = 1)
p_ly4
#since only undiluted RE are relevant, no ranges for TRD for LY
```


```{r ly2, fig.width = (5/12*3.5), fig.height = 3.5, message = FALSE, warning = FALSE}
lyc4 <- hatch_calc(input = "input/ly_figs4.csv")
lys4 <- hatch_summ3(input = "input/ly_figs4.csv")

lyc4$conc_inh <- factor(lyc4$conc_inh, levels = c("0uM", "50uM", "500uM"), ordered = TRUE)
lyc4 <- lyc4[order(lyc4$conc_inh),]
lys4$conc_inh <- factor(lys4$conc_inh, levels = c("0uM", "50uM", "500uM"), ordered = TRUE)
lys4 <- lys4[order(lys4$conc_inh),]

S4D <- plotgrid(c = lyc4, s = lys4)
S4D + theme(axis.title.x = element_text(size = 10, hjust = 1)) + xlab("LY294,002 conc. (uM)")
```


## Ketoconazole

```{r ket1, fig.width = 10, fig.height = 7, message = FALSE, warning = FALSE}
ke_c <- hatch_calc(input = "input/combined_per_treatment_ketoconazole.csv")
ke_s <- hatch_summ1(input = "input/combined_per_treatment_ketoconazole.csv")
p_ke <- overview(ke_c, ke_s, xf = 5)
p_ke

#make separate overviews for solA, TRD_l and TRD_h

ke_c_solA <- ke_c[grep("TRD|PRE|8c|PRD|8b", ke_c$treatment, ignore.case = T, invert = T),]
ke_s_solA <- ke_s[grep("TRD|PRE|8c|PRD|8b", ke_s$treatment, ignore.case = T, invert = T),]

p_ke2 <- overview(ke_c_solA, ke_s_solA, xf = 5)
p_ke2

ke_c_TRDl <- ke_c[grep("TRD_l", ke_c$treatment, ignore.case = T),]
ke_s_TRDl <- ke_s[grep("TRD_l", ke_s$treatment, ignore.case = T),]

p_ke3 <- overview(ke_c_TRDl, ke_s_TRDl, xf = 5)
p_ke3

ke_c_TRDh <- ke_c[grep("TRD_h", ke_c$treatment, ignore.case = T),]
ke_s_TRDh <- ke_s[grep("TRD_h", ke_s$treatment, ignore.case = T),]

p_ke4 <- overview(ke_c_TRDh, ke_s_TRDh, xf = 5)
p_ke4

```

```{r ket2, fig.width = (5/12*9), fig.height = 3.5, message = FALSE, warning = FALSE}
kec4 <- hatch_calc(input = "input/ketoconazole_figs4.csv")
kes4 <- hatch_summ3(input = "input/ketoconazole_figs4.csv")

S4E <- plotgrid(c = kec4, s = kes4)
S4E + theme(axis.title.x = element_text(size = 10)) + xlab("ketoconazole conc. (uM)")
```


## Dafadine

```{r dafa1, fig.width = 10, fig.height = 7, message = FALSE, warning = FALSE}
dafa_c <- hatch_calc(input = "input/combined_per_treatment_dafadine.csv")
dafa_s <- hatch_summ1(input = "input/combined_per_treatment_dafadine.csv")
p_dafa <- overview(dafa_c, dafa_s, xf = 0.5)
p_dafa
```

There is no data that is important to put in supplemental figure 4